Robotic Cart System

### 2020-10-06 systemLevelFunctionalRequirements.tex
Updated block diagram
Spelling and grammar update

\title{
    \begin{center}
        \href{http://www.bradley.edu}{\includegraphics[height=1in]{figs/logoBU1-Print}}
        \vskip10pt
        \HRule \\[0.4cm]
        {\Huge \bfseries Robotic Cart System \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
        \HRule \\[0.4cm]
    \end{center}
    }
\author{Kalli Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisor}: Dr. Suruz Miah}

@@

%------------------------------------------------
\section{System Architecture}
\subsection{System Block Diagram}
The robotic cart system will be comprised of two main subsystems - a mobile cart and a remote target device. \textlangle Darrah's block description here\textrangle

A block diagram of the robotic cart system is shown in \autoref{fig:sysBlockDiag}
\begin{figure}
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=6.5in]{figs/img/sysBlockDiag}
    \caption{Block Diagram of the Robotic Cart System}
    \label{fig:sysBlockDiag}
\end{figure}

>>>>

\title{
    \begin{center}
        \href{http://www.bradley.edu}{\includegraphics[height=1in]{figs/logoBU1-Print}}
        \vskip10pt
        \HRule \\[0.4cm]
        {\Huge \bfseries Robotic Cart System \\\Large Project Statement and Functional Requirements}\\[0.4cm] % Degree
        \HRule \\[0.4cm]
    \end{center}
    }
\author{Kallistah Allen, Darrah Beebe, and Jason Braker \\ \underline{Advisor}: Dr. Suruz Miah}

@@

%------------------------------------------------
\section{System Architecture}
\subsection{System Block Diagram}
The robotic cart system will be comprised of two main subsystems - a mobile cart and a remote target device. The system, as a whole, will take into consideration the world around it and avoid obstacles while trying to follow the remote target.  The system will also be trying to follow the remote pointer even if it loses the line of sight detection.  If the robot loses track or falls too far behind the remote, the remote will indicate this to the user.

A block diagram of the robotic cart system is shown in \autoref{fig:sysBlockDiag}
\begin{figure}[b]
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=6.5in]{figs/system_block_diagram}
    \caption{Block Diagram of the Robotic Cart System}
    \label{fig:sysBlockDiag}
\end{figure}
